\documentclass{standalone}

%\usepackage{tabular}
\begin{document}
 
\renewcommand*\thesection{\arabic{section}}

\begin{center}

This Agreement is dated and in effect as of the [Nth of MONTH, YEAR], between:\\
\vskip 1cm

{\bf Business Name\\ Address  St.\\ West Sahara, WA 02123\\}

(hereinafter the ``Buyer'').  

and\\

\vskip 1cm

{\bf  RITES Ltd.\\  Plot 1, Sector 29, Gurgaon 122001.\\ India\\}
\vskip 1cm
(hereinafter the ``Seller''), 

\vskip 2cm

\end{center}


\section{Agreement}

THIS AGREEMENT (?Agreement?) is entered into this 10 day of October, 2014 (Date of signing of Agreement), between Organisation Commune Benin-Niger de Fer et des Transports (OCBN), hereinafter referred to as ?the Buyer?, having its principal place of business at B.P. 16, Cotonou, Benin and RITES Ltd, (hereinafter referred to as ?the Supplier?) having its office located at RITES Bhawan, Plot No. 1, Sector 29, Gurgaon (Haryana) 122 001, India.
\newline
WHEREAS, the Client wishes to have the supplier perform the services hereinafter referred to, and 
\newline
WHEREAS the Supplier is willing to perform these services.
\newline
NOW THEREFORE THE PARTIES hereby agree as follows:


\section{Services:}

The Supplier shall supply Six (6)  New Meter Gauge Railway Coaches with maintenance spares, CIF, Cotonou, Benin  as per details  specified in Annexures ?A? \& ?B? which are made an integral part of this Contract. 


\section{Delivery Period:}

On receipt of technically and commercially clear order, establishment of Letter of Credit and receipt of mobilization advance by RITES by 15.07.2009, the coaches shall be shipped from Indian Port within fourteen (14) months i.e. by 15.09.2010.

In case of delay in receipt of technically and commercially clear order, establishment of Letter of Credit and receipt of mobilization advance by RITES beyond 15.07.2009,  Prices and Delivery Period shall be negotiated afresh and the contract amended suitably.

\section{Contract  Value: }

US \$ 2,545,000/- (US\$ Two Million Five Hundred Forty Five Thousand only).


\section{Terms of  Payment:}

All Payments shall be made either by telegraphic transfer of the money to RITES? account in the bank specified by RITES or through an at sight, irrevocable, without recourse, Letter of Credit established through a first class internationally renowned bank.


\section{Schedule of Payments}

i 40\% of the Contract Value shall be paid as an advance towards the cost of mobilization through telegraphic transfer of the money to RITES bank account, upon   signing the contract for the supply of the coaches. RITES will submit a Bank Guarantee valid for one year for this amount in format at Appendix ?D?.

ii 60\% of the Contract Value through an irrevocable \& confirmed Letter of Credit (LC) upon submission of shipping documents.

\section{Performance Standards:}

The   Supplier   undertakes to   perform the Services with the highest standards of professional and ethical Competence and integrity. 

\section{Confidentiality:}

The Supplier shall not disclose any proprietary or confidential information relating to the Services of this Agreement or the Client?s business or operations without the prior written consent of the Client.


\section{Insurance:}

Coaches and spares shall be fully insured by the Supplier until completion of delivery on board the ocean going vessel (nominated by the Supplier) at the Indian port of shipment. The Supplier shall further fully insure the consignment from the Port of Shipment (Indian Port), till landed in the quay at Cotonou, Benin.

\section{Assistant to be provided by Client:}

The Client shall provide all necessary assistance to the Supplier for proper execution of the agreement.


\section{Law Governing Contract and Language:}

The Agreement shall be governed by laws of Benin and the Language of the Agreement shall be English and translated in French. In case of any discrepancy between English and French versions, English version shall prevail.


\vspace{1cm} 

\noindent The undersigned agrees to the terms of this agreement on behalf of his or
her organization or business.\\


%\begin{tabular}{l l }
\begin{tabular}{p{5cm}p{5cm}}
\hline

for and On behalf of the Buyer: 	& for and On behalf of the Seller 	\\
				&						\\
				&				\\
Signed by RIGOBERT A. AZON 	& Signed by S.B. Mallick  	\\
Title Director General,		& Title Director Technical 	\\
OCBN, Benin 			&  RITES Ltd., India 		 \\
\rule{6cm}{.2pt} 		& \rule{6cm}{.2pt} 		\\
Date: \rule{2.4cm}{.2pt}	& Date: \rule{2.4cm}{.2pt}	\\
CLIENT REPRESENTATIVE      	& SELLER REPRESENTATIVE		\\
				&				\\
Witness				& Witness			\\
\rule{6cm}{.2pt} 		& \rule{6cm}{.2pt} 		\\
\rule{6cm}{.2pt} 		& \rule{6cm}{.2pt} 		\\
\hline
\end{tabular}





 

\section*{Enclosures:}

Annexure A : General   Provisions\\
Annexure B:  Special Provisions\\
Appendix  A :   Schedule of  articles to be supplied and their value\\
Appendix  B:   Technical specifications of coaches\\
Appendix  C:  Packing and marking instructions\\
Appendix  D:  Specimen Bank Guarantee for Advance Payment\\

\end{document}
