\documentclass[12pt]{book}  %article} 
%{hitec} %article} %\title{MWE} \usepackage{blindtext} \usepackage{graphicx} 
\usepackage{standalone}
\usepackage{geometry}
\geometry{letterpaper,tmargin=1in,bmargin=1in,lmargin=1.4in,rmargin=1.4in}
\usepackage{invoice}



\begin{document}

\begin{center}
{\Large Offer for Sale of Indian Railways Standard MG Coaches Draft Agreement}
\end{center}

\hrule height .1mm

\vspace{.5cm}

\input{chp/CAcoachsupply.tex}

\newpage

\input{chp/SCCcoachsupply.tex}


ANNEXURE B

SPECIAL PROVISIONS


1.	TECHNICAL DOCUMENTATION TO BE FURNISHED BY SELLER

(i) The Supplier shall furnish a complete set of Maintenance Instruction Manuals, which shall contain all instructions, data and diagrams/ sketches required for maintenance repairs of the Coach. 
(ii) The Supplier shall provide spare parts catalogue to facilitate identification of parts for ordering the replacements. 

2.	DISCREPANCIES IN MATERIAL SUPPLIED

The dispatch of material for Coaches and all other Articles shall be in accordance with the invoice of the relevant consignment. If there were any discrepancies such as incorrect stores, shortage of quantity, etc., the regularisation of such discrepancies shall be taken up to replacement of incorrect stores, fulfillment of shortage quantity, return of incorrect stores to the Supplier, etc., shall be borne by the Supplier.

3.	FACILITIES

(i) 	The Buyer shall provide the Supplier free of cost, reasonable requirements, such as Working space, Test Equipment, storage Accommodations, Electric Power, Fuel oil, Local Technicians and unskilled labour during trials and commissioning of the coaches.
(ii)	The Supplier shall be allowed to import necessary equipment, tools and test instruments for test run of Coaches and commissioning of the machines for the use of Suppliers Personnel for the successful completion of the work in Benin. The cost of the equipment and their insurance charges for shipping to Benin shall be borne by the Supplier. The list of equipment to be imported shall be submitted to the Buyer. Buyer will arrange for waival or payment of Custom Duty and any other local taxes for test equipment and special commissioning tools.

4.	TECHNICAL CO-OPERATION

The Supplier shall arrange training in India of 3 OCBN personnel for 5 weeks in maintenance practices for the coaches being supplied. All expenses on training including the cost of international travel and training in India shall be borne by the Supplier.

5.	LIFTING DEVICE

(i) 	The Supplier shall arrange special lifting tackle for loading and unloading the coaches. 
(ii)	Lifting tackle shall be delivered with the first batch of coaches to the Buyer.

6. 	PROTECTIONS AND PACKING

Care shall be taken to ensure that all parts are adequately protected against exposure, damage and ingress of dirt \& foreign matter to working parts during the transit and shipment. 

APPENDIX ‘A’

\section{Price schedule}
SCHEDULE OF ARTICLES TO BE SUPPLIED AND THEIR VALUE
(Amount in : United States Dollars)


S.
No.
Description of Articles
Quantity
Cost per Coach CIF Cotonou, Port 
Total Cost of 38 Coaches CIF, Cotonou Port
1.
Supply and commissioning of 6 New Meter Gauge Coaches to Specifications at Appendix ‘B’ along with maintenance spares as given below :

2,545,000
a.  First Class Air Conditioned Chair Car   1585,000\\
b.  Ordinary Chair Car                      5392,000\\

%\hline

Total Cost for 6 Coaches (CIF Cotonou Port, Benin) : US\$ Two Million Five Hundred Forty Five Thousand only






\newpage
APPENDIX ‘B’
\input{chp/STRCoachMG.tex}


\newpage

APPENDIX ‘C’
\input{chp/PackLabelCoach.tex}


\newpage
APPENDIX ‘D’

\input{chp/BGformatCoach.tex}





\section{invoice}
    \begin{invoice}{Rs}{12.36}
      \ProjectTitle{Example Project}%
      \Fee{Development} {1000.00} {1}
      \Fee{Development} {1000.00} {1}
      \Fee{Development2} {1000.00} {4}
      \Fee{Development} {1000.00} {1}
      \ProjectTitle{Example Project2}%
      \Fee{Development} {1000.00} {1}
      \Fee{Development} {1000.00} {1}
      \Fee{Development2} {1000.00} {4}
      
    \end{invoice}


    
 \section{General}

If any provision of this Agreement is held by a court of competent
jurisdiction to be invalid, void, or unenforceable, the remaining provisions
will nevertheless continue in full force and effect, and the parties shall,
in good faith, attempt to modify the invalid provision so it becomes a valid
provision.

This Agreement constitutes the entire understanding and agreement of the
parties and supersedes all prior written or oral agreements with respect to
the subject matter of this Agreement. This Agreement may not be modified or
amended without the express written agreement of both parties. Waiver of any
provision of this Agreement by a party shall not constitute a waiver of any
other provision or waiver of the same provision at any other time.

[EDIT THIS NEXT SECTION FOR YOUR STATE]

This Agreement shall be governed by and construed in accordance with the
laws of the Commonwealth of Massachusetts, and both parties hereby consent
to the exclusive jurisdiction and venue of the state and federal courts of
the Commonwealth. Additionally, the parties also agree and consent to
process within or without said Commonwealth by certified mail requiring a
signed receipt.

\vspace{1cm} 

\noindent The undersigned agrees to the terms of this agreement on behalf of his or
her organization or business.\\\\

\noindent \begin{tabular}{l l l}
On behalf of the Client: & \rule{6cm}{.2pt} & Date: \rule{2.4cm}{.2pt}\\
                         & CLIENT REPRESENTATIVE      & \\\\\\
The Consultant:          & \rule{6cm}{.2pt} & Date: \rule{2.4cm}{.2pt}\\
                         & CONSULTANT NAME      & \\
\end{tabular}

\end{document}   
    
    
\section{Services}

Consultant will provide software development services for a [SHORT
  DESCRIPTION OF PRODUCT HERE].  Components and features of this site will
be determined collaboratively by Client and Consultant, and are expected to
include [KEY FEATURES IF DESIRED].

Consultant's responsibilities will include collaborating with Client to
establish software requirements and priorities based on Client's business
goals; development of software in accordance with these requirements and
priorities; deployment of such software onto internet-accessible systems;
and administration of such systems.  In support of these goals, Client is
expected to work with Consultant to set priorities, review software as it is
developed, and produce product research and specifications as required.
Client and Consultant will arrange periodic meetings and phone discussions
to support this collaboration.


\section{Compensation and Payment}

In consideration of the Consultant's services, Client will pay
Consultant at the rate of {\bf \$[BILLIONS] / hour.}

Consultant will provide an invoice to the Client at the end of each calendar
month, indicating time worked each day during that month and the
amount due.  Payment will be made to Consultant in US dollars, by check or
wire transfer, within thirty (30) days of receipt of the invoice.  Travel,
living and any related out-of-pocket expenses, if authorized in writing by
Client, will be indicated on the invoice and reimbursed at cost.


\section{Contract Length and Availability}

The full length of this contract is as follows:

Starting date is the [Nth day of MONTH, YEAR] and end date is the [Nth day of LATER MONTH, YEAR -- {\em you may also want to say that the end date is to be determined through mutual agreement or until such time as the contract is terminated per the terms described below}].

During this period, Consultant will guarantee availability of at least [SOME REASONABLE NUMBER, IF THE CLIENT CARES]
hours per week for work on tasks selected by the Client.  Client and
Consultant will review this time guarantee every two weeks and may adjust it
as agreed upon with two weeks notice.

Should the Consultant be rendered unable to work by illness, injury, or
emergency, the Consultant will notify Client at Consultant's earliest
opportunity, and the guarantee of availability will not apply during those
weeks when the Consultant is unable to work.

The Consultant and Client may specify, by advance written agreement, that no
work shall be performed and no charges assessed during certain periods when
either party is unavailable.  At present, Consultant expects to be available
for the full guaranteed time through [MONTHS]. {\em [This is where you note any vacations or schedule restrictions that you want to give the client early notice of.]}


\section{Termination}

Either party may terminate this Agreement by giving 30 days written notice
to the other of such termination. In the event that Work is postponed or
terminated at the request of the Client, Consultant shall have the right to
bill %pro rata 
for work completed through the date of that request, while
reserving all rights under this Agreement. If additional payment is due,
this shall be payable within thirty days of the Client's written
notification to stop work. In the event of termination, the Client shall
also pay any expenses incurred by Consultant.  The Client shall assume
responsibility for all collection of legal fees necessitated by default in
payment.




\section{Confidentiality}

The Client and Consultant may disclose confidential information one to the
other to facilitate work under this Agreement.  Such information shall be so
identified in writing at the time of its transmittal, and shall be
safeguarded and not disclosed to third parties by the receiving party.
Confidential information shall not include information that:

\begin{enumerate}
  \item is already known to the party to which it is disclosed; 
  \item is or becomes part of the public domain without breach of this Agreement;
  \item is obtained from third parties, which have no obligations to keep
    confidential to the parties to this Agreement. 
\end{enumerate}




\section{Permissions and Releases}

The Client agrees to indemnify and hold harmless Consultant against any and
all claims, costs, and expenses, including attorney's fees, due to materials
included in the Work at the request of the Client for which no copyright
permission or previous release was requested or uses which exceed the uses
allowed pursuant to a permission or release.  


\section{Copyright Notice [OPTIONAL - may also be a `work for hire' assignment - hack as appropriate]}

Copyright on Work is in Consultant's name.  Consultant reserves the right to incorporate the Work into projects for clients other than the Client, and reserves the right to license the Work (or components thereof) on terms of Consultant's choice without restriction.


\section{Independent Contractor}

The Client and Consultant are independent parties and nothing in this
Agreement shall constitute either party as the employer, principal or
partner of or joint venture with the other party.  Neither the Client nor
Consultant has any authority to assume or create any obligation or
liability, either express or implied, on behalf of the other.

\section{General}

If any provision of this Agreement is held by a court of competent
jurisdiction to be invalid, void, or unenforceable, the remaining provisions
will nevertheless continue in full force and effect, and the parties shall,
in good faith, attempt to modify the invalid provision so it becomes a valid
provision.

This Agreement constitutes the entire understanding and agreement of the
parties and supersedes all prior written or oral agreements with respect to
the subject matter of this Agreement. This Agreement may not be modified or
amended without the express written agreement of both parties. Waiver of any
provision of this Agreement by a party shall not constitute a waiver of any
other provision or waiver of the same provision at any other time.

[EDIT THIS NEXT SECTION FOR YOUR STATE]

This Agreement shall be governed by and construed in accordance with the
laws of the Commonwealth of Massachusetts, and both parties hereby consent
to the exclusive jurisdiction and venue of the state and federal courts of
the Commonwealth. Additionally, the parties also agree and consent to
process within or without said Commonwealth by certified mail requiring a
signed receipt.

\vspace{1cm} 

\noindent The undersigned agrees to the terms of this agreement on behalf of his or
her organization or business.\\\\

\noindent \begin{tabular}{l l l}
On behalf of the Client: & \rule{6cm}{.2pt} & Date: \rule{2.4cm}{.2pt}\\
                         & CLIENT REPRESENTATIVE      & \\\\\\
The Consultant:          & \rule{6cm}{.2pt} & Date: \rule{2.4cm}{.2pt}\\
                         & CONSULTANT NAME      & \\
\end{tabular}

\end{document}
