%RITES Limited\\

RITES Ltd., a Government of India Enterprise was established in 1974, under the aegis of Indian Railways. RITES is incorporated in India as a Public Limited Company under the Companies Act, 1956 and is governed by a Board of Directors which includes persons of eminence from various sectors of engineering and management.

RITES Ltd., an ISO 9001:2008 certified company, is a multi-disciplinary consultancy organization in the fields of transport, infrastructure and related technologies. It provides a comprehensive array of services under a single roof and believes n transfer of technology to client organizations. In overseas projects, RITES actively pursues and develops cooperative links with local consultants / firms, as means of maximum utilization of local resources and as an effective instrument of sharing its expertise.

RITES is internationally recognized as a leading consultant with operational experience of 62 countries in Africa, South East Asia, Middle East and Latin America. Most of RITES foreign assignments are for National Governments and other apex organizations.

RITES employs over 2000 staff including over 1200 specialists of high professional standing in the fields of engineering, management and planning. Besides full time professionals, RITES also has on its panel a large number of experts, whose services can be drawn upon at short notice. This provides the company unmatched strength in meeting the needs of its clients worldwide.
 
Contact Information\\

Mr. Gopal Kumar, Group General Manager(Expotech)\\
email:- gopalkumar@rites.com\\
Tel :- +91-124-2818203 \\

 