\section{RITES Limited}

\subsection{Background}

%\medskip

RITES Ltd., a Government of India Enterprise was established in 1974, under the aegis of Indian Railways. RITES is incorporated in India as a Public Limited Company under the Companies Act, 1956 and is governed by a Board of Directors which includes persons of eminence from various sectors of engineering and management.

RITES Ltd., an ISO 9001:2008 certified company, is a multi-disciplinary consultancy organization in the fields of transport, infrastructure and related technologies. It provides a comprehensive array of services under a single roof and believes n transfer of technology to client organizations. In overseas projects, RITES actively pursues and develops cooperative links with local consultants / firms, as means of maximum utilization of local resources and as an effective instrument of sharing its expertise.

RITES is internationally recognized as a leading consultant with operational experience of 62 countries in Africa, South East Asia, Middle East and Latin America. Most of RITES foreign assignments are for National Governments and other apex organizations.

\section{OUR RESOURCES}

RITES employs over 2000 staff including over 1200 specialists of high professional standing in the fields of engineering, management and planning. Besides full time professionals, RITES also has on its panel a large number of experts, whose services can be drawn upon at short notice. 
This provides the company unmatched strength in meeting the needs of its clients worldwide.



\section{Board of Directors}
\noindent

Mr. Rajeev Mehrotra , Chairman \& Managing Director\\

Mr. Arbind Kumar, Director Projects \\

Mr. Ajay Kumar Gaur, Director Finance \\

Mr. Shashi Bhushan Malik,  Director Technical \\

Mr. R. S. Kochak, Govt. Nominee Director \\

Mr. A P Dwivedi , Govt. Nominee Director   \\


{\color[rgb]{0.0,0.0,0.04}
Since the late sixties, Indian Railways have been extending technical co-operation to developing countries in the field
of railroad technology. These services made a start in Jordan and were later extended to other countries including
Iraq, Philippines, Saudi Arabia, Thailand, Iran, Ghana, Nigeria, Tanzania, Kenya, Ethiopia, Uganda, Mozambique, Sudan,
Zambia, Zimbabwe, Sri Lanka, Burma, Vietnam, Bangladesh and Mexico.}


\bigskip

{\color[rgb]{0.0,0.0,0.039215688}
With the increase in world-wide demand for professional services in various fields of transportation technology,
particularly in the context of expansion and modernization of existing transport systems, it became necessary to
channelize, on a rational basis, the export of technological know-how, expertise and special skills acquired by the
Indian Railways over the past 50 years or so. }


\bigskip

\subsection{Organization}

\bigskip

{\color[rgb]{0.0,0.0,0.039215688}
RITES Ltd, a Government of India Enterprise, was established in 1974. RITES Ltd. is incorporated in India as a Public
Limited Company under the companies Act, 1956 and is governed by Board of Directors, which includes experts/
administrators of eminence from various sectors of activities of RITES interest. }


\bigskip

{\color[rgb]{0.0,0.0,0.039215688}
RITES Ltd specializes in providing comprehensive consultancy services under a single roof and believes in sharing its
experience with client organizations. \ }


\bigskip

{\color[rgb]{0.0,0.0,0.039215688}
RITES Ltd, employs nearly 2000 staff including nearly 1200 specialists of high professional standing in the fields of
Engineering, Management, Planning and Financial analysis. Besides full time professionals, RITES Ltd., has on its panel
a large number of experts, whose services can be drawn at short notice. This provides the company an unmatched strength
in meeting the needs of the clients Worldwide.}

