\section{Consultancy fee for the study }

All experts proposed to be deputed for the project are senior and experienced personnel. The mandays rate proposed to be
charged for the services of our experts in Senegal and India are indicated below:


\tablefirsthead{}
\tablehead{}
\tabletail{}
\tablelasttail{}
\begin{supertabular}{m{1.813cm} m{7.004cm}   m{2.501cm}   m{1.229cm} m{cm}   m{-0.119cm}}

\multicolumn{5}{m{15.26cm}}{\centering \textbf{\textcolor[rgb]{0.4392157,0.1882353,0.627451}{Pricing Schedule for study}}} & \multicolumn{1}{m{-0.119cm}}{~ }\\
\hline

\centering{\bfseries S. No.} &  \centering{\bfseries Cost Element} & \centering{\bfseries Rate in US\$} & \centering{\bfseries Man days} & \multicolumn{2}{m{1.994cm}}{\centering{\bfseries Fee in US\$}}\\
\hline
\centering ( i ) & Expert in \textbf{Senegal} &  \centering 300 & \centering 60 & \multicolumn{2}{m{1.994cm}}{\centering 18000}\\
\centering ( ii ) & Expert in INDIA  & \centering 200 & \centering 10 & \multicolumn{2}{m{1.994cm}}{\centering 2000}\\
\centering ( iii ) & Travel and Miscellaneous Expenditure & \centering ~ &  & \multicolumn{2}{m{1.994cm}}{\centering ~}\\
\centering ( a) & International Travel for RITES Expert  & \centering Lump sump & ~  & \multicolumn{2}{m{1.994cm}}{\centering 20,000}\\
\centering ( b ) & Field survey, preparation of report etc. & \centering Lump sump & \centering ~ & \multicolumn{2}{m{1.994cm}}{\centering 10,000}\\
\hline
~ & {\bfseries GRAND TOTAL} &  \centering ~ & \centering ~ & \multicolumn{2}{m{1.994cm}}{\centering{\bfseries 50,000}}\\
\hline
\end{supertabular}

The Consultancy Fee for the study shall Fifty thousand US Dollars only excluding Taxes, Duties, Levies, etc. for the
work covering the scope specified.

\subsection{Schedule of Payment}

All payments shall be made in US Dollars through an irrevocable, confirmed, without recourse, payable at sight letter of
credit (LC) in favour of RITES Limited for 100\% value of the contract through a first class internationally renowned
bank having a branch office in India.

Payment against the LC shall be released as follows:


\tablefirsthead{}
\tablehead{}
\tabletail{}
\tablelasttail{}
\begin{supertabular}{m{2.199cm}	m{7.0cm}	m{4.744cm}}
\hline
{\bfseries Item No.} & {\bfseries Payment Stage} & {\bfseries Fee Payable}\\
\hline
1 & Mobilization Fee on award of work to the Consultant ~  & 40\% of the total Consultancy Fee\\
2. & On Completion of Field Survey for Feasibility Study \ and submission of the first draft report ~   &   40\% of the total Consultancy Fee\\
3. & On preparation and submission of Final Feasibility Study Report  ~   &  20\% of the total Consultancy Fee\\
\hline
\end{supertabular}


The Consultancy Fee shall be paid into an irrevocable without recourse and at sight, confirmed Letter of Credit in
favour of RITES Ltd. through an internationally reputed bank with a branch in India. 


\subsection{Bank Details for the Payments}
The RITES Bankers details are given below for establishing LC;


ADDRESS : M/s Axis Bank Ltd., SG-21 \& 22,

DLF City, Phase IV, GURGAON, HARYANA-122002

SWIFT CODE : AXISINBB131.

RITES Account No : 131020200007306



\subsection[Taxes, Duties, Levies, etc.]{\bfseries Taxes, Duties, Levies, etc.}

Service Tax: - In addition to the rates quoted by RITES the Client \ shall pay service tax including cost of
surcharge/education cess, as applicable at the time of billing as per international norms prevailing in Senegal.


The rates quoted by the Consultant do not include any taxes direct or indirect leviable under international or local
acts or Rules, Octroi, Toll, Royalties etc. and similar inputs that may be prevailing from time to time in respect of
land structure and all materials supplied in the performance of this contract. \ The taxes and any additional taxes in
future, duties, octroi, royalties etc. levied under international or local norms shall be borne by the Client..


RITES shall be paid for any additional services, not included in the scope of work, at mutually agreed additional fees.

\subsection[Reworks]{\bfseries Reworks}


Ordinarily no modifications are expected after approval by the Client. however in case any rework is desired by the
Client, \ subsequent to having communicated approval, then the cost of such rework will be paid at mutually agreed
rates/ fees.


