\section{The Scope of Works}

The Scope of work is as follows:
 
\begin{enumerate}
 	\item   Objective of Assignment:\\
 	The goal of the safety review exercise is to establish the concessioner's level of compliance with safety of operation requirements in railway transport service and to propose/ recommend actions to be taken for safety improvement.
 	\item   The scope of service:\\
 	The consultant shall carry our safety review of all railway assets used in provision of Railway services;
 	The adequacy of the safety programs applied\
 	The operations standards, procedures, rule and regulations; 
 	The competency and aptitude of management and staff in-charge of safety critical areas in the provision of the railway services.
\end{enumerate}
 
 \subsection{Scope of Work}\label{scope-of-work}
 
 The scope includes the review / investigation in the following areas of
 performance:
 
 \begin{enumerate}
 	\item   Review status of development and implementation of effective safety management system with safe operation, Rehabilitation and Maintenance standards and procedures which also ensure that safety-critical and safety-related posts are staffed by suitably trained, qualified and experienced persons;
 	\item  To establish if all Rift Valley Railways, Kenya ( RVRK) ’s safety-related operation and maintenance information is promptly distributed and that personnel and sub-contractors are adequately briefed to ensure safety of operations;
 	\item  To ascertain if there is safe provision, control, operation and performance of the railway Services;
 	\item  To establish if there is safe provision, installation and management of infrastructure and facilities;
 	\item  To establish if Conceded Assets are maintained in a safe condition and in accordance with its obligations under the Concession Documents;
 	\item  To establish if the concessionaire Complies with the lawful directions of KR and/or a railway regulator pursuant to the provisions of the Laws of Kenya;
 	\item  To examine security status and requirements contributing to safety of operations; and Establish if concessionaire discharges its obligations as to health and safety duties and obligations under the Laws of Kenya." 
 \end{enumerate}
 The scope of the project will include but is not limited to review/investigation in the
 following areas of performance by the concessionaire:
 
 
 
 In addition, the consultant is also expected to review the
 following:\\i. RVRK's status with respect to required safety approvals
 and certification.\\ii. RVRK's Safety Policy Standards and
 Guidelines.\\iii. Planned Safety Inspections.\\iv. Risk and Occurrence
 management.\\v. Human Factors management.\\vi. Engineering and
 Operational Systems.\\vii. Materials and supplies.\\viii. Interface
 management.
 
 This review shall cover the period since the start of concession in 2006
 to 30 th May 2016.\\The safety review shall be carried out in accordance
 with TORs, KCA, KRC Act, OHS Act, Original Equipment Manufacturer (OEM)
 specifications and KR adopted rule books in the case of locomotives and
 rolling stock and for train operations.\\The consultant will carry out
 examination of equipment, undertake train tests, investigate operation
 controls, management and staff interviews and RVRK's operating and
 maintenance information and records as the consultant considers
 necessary under the circumstances. In conducting the safety review,
 special attention should be paid to the KCA provisions with respect to
 RVRK's mandatory obligations in safety management.
 
 \subsection{QUALIFICATION REQUIREMENTS}\label{qualification-requirements}
 
 Consultants should provide information demonstrating that they have the
 required qualifications and relevant experience to perform the Services.
 
 The shortlisting criteria are:
 
 i) The consultant firm must comprise a
 multidisciplinary team of Professional Railway Experts with at least 10
 years' experience in railway operations and maintenance and registered
 with EBK.\\
 ii) The firm must provide evidence of experts having  practiced: railway safety inspection, railway maintenance engineering of
 tracks/rolling stock/signals/operations as a requirement in order to  deliver on KR expectations.\\
 
 iii) The consultant must comprise a team  that shall have as a minimum Traction/Rolling stock Engineer, Track  Engineer, Train operations Expert and Signalling and Communications  Engineer to ensure key issues for safety assessment are handled by  appropriate specialists. \\
 iv) Proof of experience (CVs) in performing  assignments similar in nature for reputable organizations in the past as  an employee or consultant shall be submitted for Key experts.\\
 v) List  of current and past railway safety engagements, names of the  organizations, contacts and nature of the assignment shall be attested  to in the expert CV.\\
 vi) The lead expert shall be required to possess the following:-\\
 a. Relevant Engineering Degree or equivalent;\\
 b. Prior  professional experience in similar exercises;\\c. Should have undertaken
 at least three (3) assignment of a similar nature in the past;\\
 d. Excellent writing, communication and analytical skills;\\
 e. Good team leader\\
 f. Proficient in English; proficiency in Kiswahili but not essential;\\
 g. Be a person of high integrity.\\
 vii) The consultancy firm  should be registered with the Engineers Board of Kenya as an Engineering  Consulting Firm.\\
 viii) The Consultant or Consortium shall provide  professionally qualified staff to provide the services with the Team
 Leader/Key Experts listed in Table 1 below as a minimum requirement. The  CV's of each Expert shall be given in the format of Form 3, Appendix A4.
 
 In addition, as a sign of commitment each of the Five Experts will be
 required to complete the Declaration of Staff Availability form (Form 4
 Appendix A5).
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 

\section{APPROACH AND METHODOLOGY}

\subsubsection{The selection and formation of the Team of Experts}


RITES Ltd shall form a multidisciplinary team of key experts including in-house experts consultants from Indian Railways
and the relevant Industry, with international experience representing:
 

i)For deciding the type and number of rolling stock (including locomotives) required, the traffic projections will
have to be analysed and studied. The performance and capacity of existing rolling stock will have to be assessed and to
overcome the shortfall, additional rolling stock(type wise and numbers) will have to be procured/leased. While
recommending the additional rolling stock the suitability of different types of rolling stock as regards
specifications, performance, cost, etc. will have to be matched with the local requirement.

ii) The maintenance facilities required will be worked out after studying the existing maintenance practices and
facilities. The following major activities will be studied


 


\section{Client Cooperation}
\subsection{Assistance and information required from Client}

 
Assistance required from the Client


The client is requested to provide all necessary assistance to RITES' personnel in obtaining the requisite permits,
permissions and data, wherever necessary.


Client will nominate a coordinating official with RITES. He will also assist in organizing various meetings, collection
of data and reports and interaction with the relevant officials. Client will also provide competent interpretors /
translators having technical background for communication between RITES team \& Local official of the Clients .


The client will provide:

\begin{enumerate}
\item Reasonable Safety and Security for RITES' experts when conducting their survey of the new lines.
\item Making available the necessary documents and access to resources of Rift Valley Railway.
\item A qualified suitable person to assist the RITES personnel during field visits \& site verifications.
\item Fully furnished room / office accommodation of a suitable size for working.
\item Liaison, permission and coordination with Govt. \ as required for the study report.
\end{enumerate}


The client will provide necessary drawings, specifications of standard designs, other drawings and information as
available with it. 

 

\subsubsection[Information and Records / Data \ normally includes the following]{Information and Records / Data  normally includes the following}
\begin{enumerate}
\item Schedule of Dimensions
\item Maximum Moving Dimensions 
\item Track details:
\end{enumerate}
\begin{enumerate}
\item  Rail - Poundage (lb/yard, kg/m) and its age
\item  Sleepers - Type (wooden/steel/cast iron) and its age. 
\item  Fastening
\end{enumerate}

\begin{enumerate}
\item Point \& crossings -- Type, permissible speed
\item Railway System map showing name of stations \& their chainages
\item Railway time table showing sanctioned speed, stations \& its inter distances, speed restrictions, infringement to
schedule of dimensions etc. 
\item Maintenance organization and equipments
\item List of curves showing location/ chainages, degree/radius
\item List of gradients
\item Spot of bad/weak formation
\item Copy of manual/codes, standard drawings.
\item \ Index plan \& index section
\item \ Yard plans
\item \ Detailed plan \& L- section 
\item Previous reports, if any 
\item Past relevant reports/data to be made available by the Client.
\item Details of the type of locomotives and passenger cars available. The technical details about the type of coupler,
bearing, wheel, brakes, buffer height.
\item Locations of maintenance facilities for locomotives and passenger cars being and shall be done based on
operational requirements.
\item Technical Specification of the Rolling Stock and the Maintenance Manuals
\end{enumerate}




\section{TIME PERIOD AND DELIVERABLES}


The time required will be 6(Six) months.


\begin{enumerate}
\item A Draft Report will be submitted within 2 months after commencement of work.
\item It is assumed that client will give its \ comments on this draft \ \ report within one month of submission of
report
\item A Final Report will be submitted within a month of receipt of comments. The final report will be submitted even if
there are no comments on draft report.
\end{enumerate}

\section{EXPRESSION OF INTEREST}\label{expression-of-interest}

\subsection{SAFETY REVIEW OF RAILWAY OPERATIONS BY RIFT VALLEY RAILWAYS
	(KENYA) LTD OVER THE CONCEDED RAILWAY NETWORK IN
	KENYA}\label{safety-review-of-railway-operations-by-rift-valley-railways-kenya-ltd-over-the-conceded-railway-network-in-kenya}

The Kenya Railways (KR) is a State Corporation established under the
Kenya Railways Act Cap 397. The Corporation is mandated to provide rail
and inland waterway transport service. KR has a total railway network of
1920 kilometres single track meter gauge. The existing railway network
is used to provide freight transport services, commuter rail services in
Nairobi and long distance passenger services from Nairobi to Mombasa.

The Government of Kenya (GoK) and Kenya Railways (KR) conceded railway
operations in a vertically integrated arrangement covering all railway
Operations and Maintenance (Technical, operations and commercial) to
Rift Valley Railways (Kenya) Ltd (RVRK) in November 2006. The concession
is contracted under three sets of documents, namely; Kenya Concession
Agreement 2006 (KCA), Kenya Direct Agreement (DA) and Interface
Agreement (IA) for the two countries Kenya and Uganda who undertook a
joint concession.

Following a spate of serious railway accidents, the compliance with the
obligations critical to rail safety under the Kenya Concession Agreement
by RVRK as the Concessionaire is now a subject of safety review. To
implement this safety review the grantor of the concession (GoK/KR)
seeks responses from suitably qualified, experienced consultancy
firms/joint ventures to undertake the safety review of RVRK railway
operations.

KR therefore invites eligible firms to express their interest to provide
the above consultancy services.

\section{1. OBJECTIVES OF THE
	ASSIGNMENT}\label{objectives-of-the-assignment}

The goal of the safety review exercise is to establish the
concessionaire's level of compliance with safety of operations
requirements in railway transport services and to propose/recommend
actions to be taken for safety improvement.

\section{2.SCOPE OF SERVICES}\label{scope-of-services}

The Consultant shall carry out safety review of all railway assets used
in the provision of railway services; the adequacy of the safety
programs applied; the operating standards, procedures, rules and
regulations; the competency and aptitude of management and staff
in-charge of safety critical areas in the provision of the railway
services. The scope of the project will include but is not limited to
review/investigation in the following areas of performance by the
concessionaire:

\begin{enumerate}

	\item  	Review status of development and implementation of effective safety
	management system with safe operation, Rehabilitation and Maintenance
	standards and procedures which also ensure that safety-critical and
	safety-related posts are staffed by suitably trained, qualified and
	experienced persons;
	\item 	To establish if all RVRK's safety-related operation and maintenance
	information is promptly distributed and that personnel and
	sub-contractors are adequately briefed to ensure safety of operations;
	\item 	To ascertain if there is safe provision, control, operation and
	performance of the railway Services;
	\item 	To establish if there is safe provision, installation and management
	of infrastructure and facilities;
	\item 	To establish if Conceded Assets are maintained in a safe condition and
	in accordance with its obligations under the Concession Documents;
	\item 	To establish if the concessionaire Complies with the lawful directions
	of KR and/or a railway regulator pursuant to the provisions of the
	Laws of Kenya;
	\item 	To examine security status and requirements contributing to safety of
	operations; and
	\item 	Establish if concessionaire discharges its obligations as to health
	and safety duties and obligations under the Laws of Kenya."
\end{enumerate}

In addition, the consultant is also expected to review the following:
RVRK's status with respect to required safety approvals and
certification. i. RVRK's Safety Policy Standards and Guidelines. ii.
Planned Safety Inspections. iii. Risk and Occurrence management. iv.
Human Factors management. v. Engineering and Operational Systems. vi.
Materials and supplies. vii. Interface management.

This review shall cover the period since the start of concession in 2006
to 30 th May 2016.

The safety review shall be carried out in accordance with TORs, KCA, KRC
Act, OHS Act, Original Equipment Manufacturer (OEM) specifications and
KR adopted rule books in the case of locomotives and rolling stock and
for train operations. The consultant will carry out examination of
equipment, undertake train tests, investigate operation controls,
management and staff interviews and RVRK's operating and maintenance
information and records as the consultant considers necessary under the
circumstances. In conducting the safety review, special attention should
be paid Page 2 of 11to the KCA provisions with respect to RVRK's
mandatory obligations in safety management.

\section{3. QUALIFICATION
	REQUIREMENTS}\label{qualification-requirements}

Consultants should provide information demonstrating that they have the
required qualifications and relevant experience to perform the Services.
The shortlisting criteria are:

\begin{enumerate}

	\item 	The consultant firm must comprise a multidisciplinary team of
	Professional Railway Experts with at least 10 years' experience in
	railway operations and maintenance and registered with EBK.
	\item 	The firm must provide evidence of experts having practiced: railway
	safety inspection, railway maintenance engineering of tracks/rolling
	stock/signals/operations as a requirement in order to deliver on KR
	expectations.
	\item 	The consultant must comprise a team that shall have as a minimum
	Traction/Rolling stock Engineer, Track Engineer, Train operations
	Expert and Signalling and Communications Engineer to ensure key issues
	for safety assessment are handled by appropriate specialists.
	\item 	Proof of experience (CVs) in performing assignments similar in nature
	for reputable organizations in the past as an employee or consultant
	shall be submitted for Key experts.
	\item 	List of current and past railway safety engagements, names of the
	organizations, contacts and nature of the assignment shall be attested
	to in the expert CV.
	\item 	The lead expert shall be required to possess the following:-
\end{enumerate}

\begin{enumerate}

	\item	Relevant Engineering Degree or equivalent;
	\item	Prior professional experience in similar exercises;
	\item	Should have undertaken at least three (3) assignment of a similar 	nature in the past;
	\item	Excellent writing, communication and analytical skills;
	\item	Good team leader
	\item	Proficient in English; proficiency in Kiswahili but not essential;
	\item	Be a person of high integrity.
\end{enumerate}


The consultancy firm should be registered with the Engineers Board of
	Kenya as an Engineering Consulting Firm.


viii) The Consultant or Consortium shall provide professionally qualified
staff to provide the services with the Team Leader/Key Experts listed in
Table 1 below as a minimum requirement. The CV's of each Expert shall be
given in the format of Form 3, Appendix A4. In addition, as a sign of
commitment each of the Five Experts will be required to complete the
Declaration of Staff Availability form (Form 4 Appendix A5).

\section{Table 1:}\label{table-1}

\subsection{Minimum Qualifications and Experience of Team Leader/Key
	Experts}\label{minimum-qualifications-and-experience-of-team-leaderkey-experts}

\subsection{1 Team Leader/Key Expert Minimum
	Education}\label{team-leaderkey-expert-minimum-education}

1 Team Leader/Lead Expert

\subsection{2 Key expert 1: Traction and Rolling Stock
	Expert}\label{key-expert-1-traction-and-rolling-stock-expert}

Specialisation and Experience

University degree in Experience in any of the areas for Railway Safety
the key experts. Inspectorate work inclusive of safety analysis and
reporting General management

experience

University degree in Experience in Mechanical/Electrical design,
construction engineering.and maintenance of railway traction and rolling
stock.

Railway accidents investigation

experience.

Years of Experience Related

Number of Projects/Assignment 10-years 3 10-years 3

\subsection{3 Key expert 2:}\label{key-expert-2}

Railway track and structures expert r University degree in civil
engineering.

Experience in design, construction and maintenance of railway tracks and
structures. Railway accidents investigation experience. 10-years 3

\subsection{4 Key expert 3:}\label{key-expert-3}

Signalling and telecommunications expert University degree in
Electrical/related engineering with specialization in railway signalling
and/or telecommunications. Experience in 10-years design, construction
and maintenance of railway signalling systems and/or telecommunications.
Railway accidents investigation

experience. 3

\subsection{5 Key expert 4: Train operations
	expert}\label{key-expert-4-train-operations-expert}

University degree in related fields. Experience in railway traffic
operations. Railway accidents investigation

experience. 3 10-years

1ix) The consultancy firm should provide a list of names and CV's of Key
Personnel expected to take part in the assignment, with minimum of ten
(10) years relevant working experience each and duly registered with the
relevant professional bodies.

\begin{enumerate}
	\item 	The consultancy firm should provide a certified copy of certificate of 	incorporation;
\end{enumerate}

\begin{enumerate}
	\item	The consultancy should provide copies of PIN and VAT Registrations and
	Valid Tax Compliance Certificate.
	\item	Consultants may associate with other firms in the form of a joint
	venture or a sub- consultancy to enhance their qualifications. Local
	consultancy firms will qualify for standard preference marks in line
	with PPAD Act 2015 clause 86(2). Applicants who download the EOI from
	the website and intend to submit EOI MUST register their interest
	immediately by sending an email to
	\href{mailto:procure@krc.co.ke}{procure@krc.co.ke} stating their names
	and address. Please note that any clarification or additional
	information will only be sent to firms that will have so registered.
\end{enumerate}

Expressions of Interest shall be returned in a plain sealed plain
envelope, bearing one (1) original and five (5) copies of the EOI, shall
be clearly marked

``KRC/PLM/38/15-16: SAFETY REVIEW OF RAILWAY OPERATIONS BY RIFT VALLEY
RAILWAYS (KENYA) LTD OVER THE CONCEDED RAILWAY NETWORK IN KENYA''
addressed to:

THE MANAGING DIRECTOR

KENYA RAILWAYS

P.O. Box 30121-00100

NAIROBI

And shall be submitted in the Tender Box on the Ground floor, Kenya
Railways Headquarters, Workshops Road off Haile Selassie Avenue,
Nairobi, not later than 10.00 am (East African time), on April 09, 2016

Interested Firms may seek further clarification or information by
sending an email to \href{mailto:procure@krc.co.ke}{procure@krc.co.ke}
or in writing to the above address to be received not later than March
31, 2016.

L. NJOROGE

PROCUREMENT MANAGER

DATE: 09-03-16

\section{APPENDIX A: INFORMATION \& GUIDANCE TO APPLICANTS FOR
	COMPLETING
	EOI}\label{appendix-a-information-guidance-to-applicants-for-completing-eoi}

\subsection{1. DEFINITIONS}\label{definitions}

``imilar Assignment‟: means an assignment in railway safety undertaken
in the railway industry.

``Related Projects'': means assignments related to the specialisation
and experience of the Experts indicated in Table 1. required

``Lead Firm'' If in consortium, firm that will assume leadership of the
consortium for and on behalf of consortium and submit the EOI on their
behalf.

\section{FORMAT FOR THE SUBMISSION OF CONSULTANT/LEAD FIRM‟S EXPERIENCE
	(FORM
	2)}\label{format-for-the-submission-of-consultantlead-firms-experience-form-2}

Using the format below, provide information on EACH similar assignment
for which the lead firm either individually, as corporate entity or in
association was legally contracted {[}see item 3 (iv) and (v) of the
EOI{]}

\begin{center}\rule{3in}{0.4pt}\end{center}

\section{Form 2: Firm's Experience}\label{form-2-firms-experience}

Table No 1

Assignment name:

Country:

Location of assignment within country:

Professional Staff provided by Your Firm entity (profiles):

Name and reference of Client:

Client's contact person for the assignment:

Address of Client:

No. of staff-months:

Duration of the assignment (months):

Start date (month/year): Approximate value of Services provided (Kshs):

Completion date (month/year):

Name of associated consultants, if any:

No. of months of Professional Staff provided by the Associated
Consultants:

Name of Senior Staff (Project Director/Coordinator, Team Leader)
involved and functions

performed:

Narrative description of Project:

Description of actual services provided by your staff within the
assignment:

Signature of the authorized representative of the firm:

Full name of authorized representative:

Date:

NOTARY PUBLIC/ COMMISSIONER OF OATHS:

NAME:

STAMP:

DATE:

\section{3. FORMAT FOR THE SUBMISSION OF CURRICULUM VITAE (CV) FOR EACH
	OF THE PROPOSED TEAM LEADER/KEY EXPERTS (FORM
	3)}\label{format-for-the-submission-of-curriculum-vitae-cv-for-each-of-the-proposed-team-leaderkey-experts-form-3}

Proposed Position:

Name of Firm:

Name of Key Expert:

Profession:

Date of Birth:

Years of experience in Railway Operations:
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

Nationality:

Membership in Professional Societies:

Detailed Tasks Assigned:

Key Qualifications \& Experience:

(Give an outline of Key Expert's experience and training most pertinent
to tasks on assignment. Describe degree of responsibility held by Key
Expert on relevant previous assignments and give dates and locations).

Education: (Summarize college/university and other specialized education
of Key Expert, giving names of schools, dates attended and degree{[}s{]}
obtained.)

Employment: (Starting with present position, list in reverse order every
employment held. List all positions held by Key Expert since graduation,
giving dates, names of employing organizations, titles of positions
held, and locations of assignments.)

Certification: I, the undersigned, certify that these data correctly
describe me, my qualifications, and my experience

(Signature of Key Expert):
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_Date:
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

(Signature of the authorized representative of the firm):
\_\_\_\_\_\_\_\_ Date: \_\_\_\_\_\_\_\_\_

Full name of Key Expert:
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

Full name of authorized representative:
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

\section{4. FORMAT FOR THE DECLARATION OF STAFF AVAILABILITY FOR TEAM
	LEADER/KEY EXPERT (FORM
	4)}\label{format-for-the-declaration-of-staff-availability-for-team-leaderkey-expert-form-4}

I, the undersigned, certify that should we be awarded the contract for
the CONSULTANCY SERVICES FOR SAFETY REVIEW OF RAILWAY OPERATIONS BY RIFT
VALLEY RAILWAYS(KENYA) LTD OVER THE CONCEDED RAILWAY NETWORK IN KENYA, I
shall be available for the assignment as \ldots{}

(state position)

{[}see item 3(viii) of the EOI{]}.

(Signature of key expert): \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ Date:
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

(Signature of the authorized representative of the firm): \_\_\_\_

Date: \_\_\_\_\_

Full name of key expert:

Full name of authorized representative:

\section{5. FORMAT FOR THE ADDRESS \& CONTACT DETAILS FOR CONTACT PERSON
	(FORM
	5)}\label{format-for-the-address-contact-details-for-contact-person-form-5}

I, the undersigned being the Authorized Representative of the
Consultant/Lead Firm, certify that the undersigned of details given
below shall be our contact person for the purpose of this EOI.

Name of Contact Person:

Physical Address or Post Office Box of Contact Person:

Telephone:

Email:

Fax:

Name \& Signature of the Authorized Representative of the firm
\ldots{}\ldots{}\ldots{}\ldots{}\ldots{}\ldots{}\ldots{}\ldots{}\ldots{}\ldots{}\ldots{}\ldots{}..

Date:
\ldots{}\ldots{}\ldots{}\ldots{}\ldots{}\ldots{}\ldots{}\ldots{}\ldots{}\ldots{}\ldots{}
