

{\bfseries\color[rgb]{0.4392157,0.1882353,0.627451}
7.4\ \ Payment of Consultancy Fee}


\bigskip

The Consultancy Fee shall be paid into an irrevocable without recourse and at sight, confirmed Letter of Credit in favor
of RITES Ltd. through an internationally reputed bank with a branch in India.


\bigskip

{\bfseries\color[rgb]{0.4392157,0.1882353,0.627451}
7.5\ \ Taxes, Duties, Levies, etc.}


\bigskip

Service Tax: - In addition to the rates quoted by RITES the DRC Govt. shall pay service tax including cost of
surcharge/education cess, as applicable at the time of billing as per international norms prevailing in DRC.


\bigskip

The rates quoted by the Consultant do not include any taxes direct or indirect leviable under international or local
acts or Rules, Octroi, Toll, Royalties etc. and similar inputs that may be prevailing from time to time in respect of
land structure and all materials supplied in the performance of this contract.


\bigskip

Any additional taxes, duties, octroi, royalties etc. levied under international or local norms shall be borne by the DRC
Govt.

Running Payment shall be made to RITES as per the schedule mentioned above on completion of the various
activities/deliverables. \ Payments shall be made by DRC Govt., within 7 days of receipt of invoice submitted by RITES.


\bigskip

RITES shall be paid for any additional services, not included in the scope of work, at mutually agreed additional fees.


\bigskip

{\bfseries\color[rgb]{0.4392157,0.1882353,0.627451}
7.6\ \ Rework:}


\bigskip

Ordinarily no modifications are expected after approval by DRC Govt. however in case any rework is desired by DRC Govt.
subsequent to having communicated approval, then the cost of such rework will be paid at mutually agreed rates/ fees.
